\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2018-10-26 bare_conf.tex
few sentences added to additionally connect Method and Results.

%Andrius: If we leave this section in manuscript, we should probably have a section addressing the findings of the reviews in the Results section.
%Darius
To have an overview of research progress on assistive technologies for the blind in the last ten years, a systematic literature review in three major research databases (Medline, IEEE xplore and ACM DL) was conducted. It revealed increasing research interest in the field (84 related publications were identified, while 17 were characterized as highly relevant for this project). 
%we carried out  systemic review of research articles in databases like  Medline, IEEE xplore, ACM DL.  
Systemic review of the relevant patents and patent applications worldwide was performed using online services of the following databases: EspaceNet, GooglePatents, USPTO, PatentScope, FreePatentsOnline. It revealed several main technological trends in the area of assistive technologies for the blind persons. 
Based on the aforementioned methodical reviews, some our insights are presented in the Results section.

@@

User-centered design sessions with visually impaired persons provided substantial input for the design of the proposed system (Fig.~\ref{fig:schematics}). The process made it clear that understanding of the user needs was limited in the project team. Based on the results of the user-centered design process, we present the outline of the system for impaired human vision compensation.

@@

\section{Discussion}
\label{sec:discussion}
%Didzioji Discussion teksto dalis man labiau tinka prie Results/Conclusion. Gal galim padiskutioti daugiau apie Limitations, Future Implications, Lessons Learned ar pan... Cia galime savo siuloma sistema lyginti su anksciau publikuotais rezultatais.

%In this article we outlined an idea of complex computer vision-based sensor architecture, which may help to partially compensate impaired or lost human sight.

@@

% live video pakeiciau i  image or video, mano nuomone ne taip ambicingai skamba.

@@

%our approach is advantageous, since it does not rely only on computational capacity of mobile handset. Such a combination of mobile interface and remote vision processor will be even more efficient in the future, with switching of the mobile networks to 5G.

@@

%Andrius: galima butu paminet limited knowledge on tactile interfaces for navigation purposes, placement, frequences, strenths, etc...

@@

%The developed head-mounted tactile device is developed for head position and orientation tracking and could capture an image in front of visually impaired people. The tactile device with integrated 3D deph camera is integrated with smartphone by bluetooth which could preprocess the labeled image features. The developed high quality self navigation system is based on the computer vision methods especially enhancing the capabilities to detect and classify objects (e.g bus station, street crossings, ) with their surrounding objects. The authors expect to increase the capabilies of potentially blind to secure navigate especially for the planed destination (e.g. "home-office"). Work left (outdoor/indoor) etc.

% conference papers do not normally have an appendix

% use section* for acknowledgement
\section*{Acknowledgment}
This research is/was funded by the European Regional Development Fund according to the supported activity ‘Research Projects Implemented by World-class Researcher Groups’ under Measure No. 01.2.2-LMT-K-718.

>>>>

%Andrius: If we leave this section in manuscript, we should probably have a section addressing the findings of the reviews in the Results section.
%Darius
To have an overview of research progress on assistive technologies for the blind in the last ten years, a systematic literature review in three major research databases (Medline, IEEE xplore and ACM DL) was conducted. It revealed increasing research interest in the field (84 related publications were identified, while 17 were characterized as highly relevant for this project). In order to better understand the applicability of modern computer vision technologies, we also conducted comprehensive analysis of recent advantages in the topic.
%we carried out  systemic review of research articles in databases like  Medline, IEEE xplore, ACM DL.  
Systemic review of the relevant patents and patent applications worldwide was performed using online services of the following databases: EspaceNet, GooglePatents, USPTO, PatentScope, FreePatentsOnline. It revealed several main technological trends in the area of assistive technologies for the blind persons. 
Based on the aforementioned methodical reviews, some our insights are presented in the Results section.

@@

User-centered design sessions with visually impaired persons and analysis of aforementioned data sources provided substantial input for the design of the proposed system (Fig.~\ref{fig:schematics}). The process made it clear that understanding of the user needs was limited in the project team. Based on the results of the user-centered design process and conducted publication and patent analysis, we present the outline of the system for impaired human vision compensation.

@@

\section{Discussion}
\label{sec:discussion}

@@

@@

@@

@@

\section*{Acknowledgment}
This research is/was funded by the European Regional Development Fund according to the supported activity ‘Research Projects Implemented by World-class Researcher Groups’ under Measure No. 01.2.2-LMT-K-718.
